---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# calcthat

<!-- badges: start -->
<!-- badges: end -->

The goal of calcthat is to make the common calculation, subtracting minimum value from maximum value, more convenient.

## Installation

You can install the development version of `calcthat` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("April-UBC/calcthat")
```

## Usage

A fairly common task when processing data is to subtract the minimum value from the maximum value. This is what `max_minus_min()` does.

## Example

This is a basic example which shows you how to solve a common problem. In this example, the minimum value of [1] is subtracted from the maximum value of [20]:

```{r example}
library(calcthat)

max_minus_min(1:20)
```

